Notes for Week 8/26/2020 - 9/2/2020

### 2020-09-16 notes/weekly_notes/8.26.20.NotesForWeek.tex

In this week's notes, I state and prove all results regarding graph Sobolev semi-norms that we need for our graph regression work.

@@

When $s > 1$, in order to obtain the desired upper bound on the graph Sobolev semi-norm we must make some additional assumptions regarding the behavior of $f_0$ near the boundary of $\Xset$, as well as on the smoothness of the density function $p$.
\begin{theorem}
	\label{thm:graph_sobolev_seminorm}
	For some integer $s > 1$, suppose that the density $p \in C^{s - 1}(\Xset,p_{\max})$ and $f \in H_0^s(\Xset,M)$, and additionally that the domain $\Xset$ is Lipschitz. Let $r = r(n)$ be a sequence of connectivity radii satisfying $r(n) \to 0$ and $r(n) \gtrsim n^{-1/(2(s - 1) +d)}$ as $n \to \infty$. Then for all $n$ sufficiently large, there exists a constant $C > 0$ which may depend only on $\Xset$ and $d$ such that
	\begin{equation}
	\label{eqn:graph_sobolev_seminorm}
	f^T \Lap_{n,r}^s f \leq \frac{C}{\delta} n^{s + 1} r^{s(d + 2)}M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{theorem}
A few remarks:
\begin{itemize}
	\item \textbf{Explain why~\eqref{eqn:graph_sobolev_seminorm} should be familiar, and a lower bound on $r$ expected.} The scaling (in $n$, $r$, and $M$) on the right hand side of~\eqref{eqn:graph_sobolev_seminorm} will be familiar to the informed reader. For sufficiently regular functions $f$, it is known \textcolor{red}{(references)} that $\frac{1}{nr^{d + 2}}\Lap_{n,r}f \to \Delta_pf$ for \textcolor{red}{$r \geq ???$}. In that light, it is perhaps reasonable to hope that when $r$ is sufficiently large, some recursive argument yields
	\begin{equation*}
	\Bigl(\frac{1}{nr^{d + 2}}\Lap_{n,r}\Bigr)^s f \to \Delta_p^qf \Longrightarrow \frac{1}{n^{s + 1} r^{s(d + 2)}} f^T \Lap_{n,r}^s f \to \int_{\Xset} f(x) \cdot  \Delta_p^qf(x) p(x) \,dx \leq c M^2.
	\end{equation*}
	\item \textbf{Explain why the actual proof is more subtle.}
\end{itemize}
The proof of Theorem~\ref{thm:graph_sobolev_seminorm} will be considerably longer than that of Lemma~\ref{lem:first_order_graph_sobolev_seminorm}. In anticipation of this proof, it will be helpful to introduce some notation. For $j \in [n]$ and a function $f: \Xset \to \Reals$, define the weighted difference operator $D_jf: \Xset \to \Reals$ to be
\begin{equation*}
\bigl(D_jf\bigr)(x) = \bigl(f(X_j) - f(x)\bigr) \frac{K_r(X_j,x)}{r^d},
\end{equation*}
and for $k \in [n]^q$ for some $q \in \mathbb{N}$, define the iterated difference operator $D_{jk}f: \Xset \to \Reals$ via the recursive relation
\begin{equation*}
\bigl(D_{jk}f\bigr)(x) = \bigl(D_j \circ D_kf\bigr)(x)
\end{equation*}
The matrix $\Lap_{n,r} \in \Reals^{n \times n}$ can then be extended to an operator over $C^{\infty}(\Xset)$, which in an abuse of notation\footnote{We repeat notation because it results in \eqref{eqn:graph_Laplacian_out_of_sample} agreeing with \textcolor{red}{(2)} in-sample, i.e. $\bigl(\Lap_{n,r}^qf\bigr)(X_i) = (\Lap_{n,r}^qf)_i$ for all $i \in [n]$.} we also denote by $\Lap_{n,r}$,
\begin{equation*}
\frac{1}{r^d}\bigl(\Lap_{n,r}f\bigr)(x) := -\sum_{j = 1}^{n} \bigl(D_jf\bigr)(x)
\end{equation*}
so that
\begin{equation}
\label{eqn:graph_Laplacian_out_of_sample}
\frac{1}{r^{dq}}\bigl(\Lap_{n,r}^qf\bigr)(x) = (-1)^q \sum_{k \in [n]^q} \bigl(D_kf\bigr)(x).
\end{equation} 
Consequently, a few standard computations show that the graph Sobolev semi-norm can be written as 
\begin{equation}
\label{eqn:graph_sobolev_seminorm_1}
f^T \Lap_{n,r}^s f = r^{ds} \cdot
\begin{dcases}
\sum_{i = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \bigl(D_kf\bigr)(X_i) \cdot \bigl(D_\ell f\bigr)(X_i),~~ & \textrm{if $s$ is even, for $q = s/2$} \\
\sum_{i,j = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \bigl(d_jD_kf\bigr)(X_i) \cdot \bigl(d_jD_{\ell}f\bigr)(X_i) \cdot K_r(X_i,X_j),~~ & \textrm{if $s$ is odd, for $q = (s - 1)/2$}
\end{dcases}
\end{equation}
where $\bigl(d_jf\bigr)(x) := f(X_j) - f(x)$ is the simple difference operator.

@@

\begin{lemma}
	\label{lem:expected_difference_sobolev}
	Let $q \geq 1$ and $s \geq 2q + 1$ be integers. The iterated expected weighted difference operator  $\Delta_r^qf(x) = \Ebb[D_kf(x)]$ for any $k \in (n)^q$. If $f \in H^s(\Xset,M)$ and $p \in C^{s-1}(\Xset,M)$,
	\begin{equation*}
	\Bigl\|\Delta_r^qf - \bigl(r^{2q} I_{2e_1}^{q}\bigr) \Delta_{p}^qf\Bigr\|_{\Leb^2(\Xset_{qr})} \leq CM \cdot
	\begin{dcases}
	r^{2q + 1},& ~~\textrm{if $s = 2q + 1$} \\
	r^{2q + 2},& ~~\textrm{if $s = 2q + 2$}
	\end{dcases}
	\end{equation*}
	where $\Xset_{qr} = \{x \in \Xset: B(x,qr) \subset \Xset\}$, and we recall that $\Delta_pf = -\frac{1}{2p}\mathrm{div}(p^2 \nabla f)$ is the density weighted Laplace operator.
\end{lemma}
\begin{lemma}
	\label{lem:expected_difference_boundary}
	Let $q \geq 1$ and $s \geq 1$ be integers. If $f \in H_0^s(\Xset,M)$ and \textcolor{red}{$p$ satisfies (P2)}, then for all $r > 0$ sufficiently small,
	\begin{equation*}
	\norm{\Delta_r^qf}_{\Leb^2(\Xset^{qr})} \leq cMr^s
	\end{equation*}
	where $\Xset^{qr} = \Xset \setminus \Xset_{qr}$.
\end{lemma}
\begin{lemma}
	\label{lem:expected_difference_lower_order_1}
	Let $I = \abs{k \cup \ell \cup i} < 2q + 1$ for given index vectors $k,\ell \in [n]^q$ and index $i \in [n]$. Then for any $f \in H^1(\Xset)$,
	\begin{equation*}
	\Bigl|\Ebb\Bigl[\bigl(D_kf\bigr)(X) \cdot \bigl(D_{\ell}f\bigr)(X)\Bigr]\Bigr| \leq C r^{2 + d(I - (s + 1))} \abs{f}_{H^1(\Xset)}^2
	\end{equation*}
	for a constant $C$ which does not depend on $f$.
\end{lemma}
A few remarks:
\begin{itemize}
	\item In~\textcolor{red}{Garcia-Trillos19}, results similar to Lemma~\ref{lem:expected_difference_sobolev} were shown, as part of the proof of pointwise convergence of the graph Laplacian $\Lap_{n,r}$ to $\Delta_p$. Those results specialize to the case $q = 1$ and $s = 3$, and assume the function $f$ is bounded in the relevant Holder rather than Sobolev norm, sufficient for their purposes but not for our own. 
	\item When the function $f$ lacks sufficiently regularity---i.e. when it has two or fewer bounded derivatives---we can no longer obtain an estimate of  $\Delta_rf$ in terms of $\Delta_pf$. However, we can still show that $\Delta_rf$ is itself bounded. For an open set $V \subseteq \Xset$, if $f \in H^{s}(V,M)$---and when $s = 2$, $p \in C^{1}(\Xset,M)$---then
	\begin{equation}
	\label{eqn:norm_expected_difference_operator}
	\norm{\Delta_rf}_{\Leb^2(V_r)} \leq c r^s \norm{f}_{H^s(V)}
	\end{equation}
	for $V_r = \set{x \in V: B(x,r) \subset V}$. We establish this fact, and bound a few related integrals, in Subsection~\ref{subsec:proof_boundedness_expected_difference_operator}.
	\item \textbf{Discuss how the analysis in \textcolor{red}{Belkin12} could conceivably lead to similar conclusions as Lemma~\ref{lem:expected_difference_boundary} under a milder assumption than zero-trace. Explain why you didn't bother to go down this road.}
\end{itemize}

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:expected_difference_boundary}}]
	When $q = 1$, we can relate the $\Leb^2$ norm of $\Delta_rf$ over $\Xset^r$ to the $\Leb^2$ norm of $f$ over $\Xset^{2r}$, as follows:
	\begin{align*}
	\Bigl\|\Delta_rf\Bigr\|_{\Leb^2(\Xset^r)}^2 & = \int_{\Xset^r} \biggl[\int_{\Xset} \bigl(f(y) - f(x)\bigr)K_r(x,y) p(y) \,dy \biggr]^2 \,dx \\
	& \leq p_{\max}^2 \int_{\Xset^r} \biggl[\int_{\Xset} \bigl(\abs{f(y)} +  \abs{f(x)}\bigr)K_r(x,y) \,dy \biggr]^2 \,dx \\
	& \overset{(i)}{\leq}  p_{\max}^2 K_{\max}^2 \int_{\Xset^r} \biggl[\int_{B(0,1) \cap (\Xset - x)/r} \bigl(\abs{f(zr + x)} +  \abs{f(x)}\bigr)\,dz \biggr]^2 \,dx \\
	& \overset{(ii)}{\leq} 2 p_{\max}^2 K_{\max}^2 \int_{\Xset^r} \nu_d^2 \bigl(f(x)\bigr)^2 \,dx + 2 p_{\max}^2 K_{\max}^2 \nu_d \int_{\Xset^r}\biggl[\int_{B(0,1) \cap (\Xset - x)/r} \bigl(f(zr + x)\bigr)^2\,dz\biggr] \,dx \\
	& \leq 2 p_{\max}^2 K_{\max}^2 \int_{\Xset^r} \nu_d^2 \bigl(f(x)\bigr)^2 \,dx + 2 p_{\max}^2 K_{\max}^2 \nu_d \int_{B(0,1)} \int_{\Xset^r} \bigl(f(zr + x)\bigr)^2\,dz \,dx \\
	& \leq 4 p_{\max}^2 K_{\max}^2 \nu_d^2 \norm{f}_{\Leb^2(\Xset^{2r})}^2
	\end{align*}
	where $(i)$ follows from change of variables and $(ii)$ from Young's and Jensen's inequality. Reasoning by induction, we see that to prove the claim of Lemma~\ref{lem:expected_difference_boundary} it suffices to establish that
	\begin{equation}
	\label{pf:expected_difference_boundary}
	\norm{f}_{\Leb^2(\Xset^{(q + 1)r})}^2 \leq c r^{2s} \norm{f}_{H^s(\Xset)}^2,
	\end{equation}
	and in Subsection~\ref{subsec:proof_sobolev_norm_boundary} we show that this inequality holds whenever $r > 0$ is sufficiently small.
\end{proof}

\begin{proof}[\textbf{Proof of Theorem~\ref{thm:graph_sobolev_seminorm}}]
	From the representation~\eqref{eqn:graph_sobolev_seminorm_1}, we have that 
	\begin{equation}
	\label{pf:graph_sobolev_seminorm}
	\Ebb\Bigl[f^T \Lap_{n,r}^s f\Bigr] = r^{ds}\sum_{i = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \Ebb\Bigl[\bigl(D_kf\bigr)(X_i) \cdot  \bigl(D_{\ell}f\bigr)(X_i)\Bigr].
	\end{equation}
	We divide into cases based on the cardinality of $\abs{k \cup \ell \cup i}$. If $\abs{k \cup \ell \cup i} = 2q + 1$, the intersection between any two of $k \in (n)^q$, $\ell \in (n)^q$, and $i \in [n]$ is empty. As a result, we can relate the expected product of difference operators to the square of the expected difference operator $\Delta_r^qf$ by applying the law of iterated expectation, resulting in
	\begin{align*}
	\Ebb\Bigl[\bigl(D_kf\bigr)(X_i) \cdot \bigl(D_{\ell}f\bigr)(X_i)\Bigr] & = \Ebb\Bigl[\bigl(\Delta_r^qf(X)\bigr)^2\Bigr] \\
	& \leq p_{\max}^2 \norm{\Delta_r^qf}_{\Leb^2(\Xset)}^2 \\
	& = p_{\max}^2 \Bigl\{\norm{\Delta_r^qf}_{\Leb^2(\Xset_{qr})}^2 + \norm{\Delta_r^qf}_{\Leb^2(\Xset^{qr})}^2\Bigr\} \\
	& \leq p_{\max}^2 \Bigl\{\norm{\Delta_r^qf}_{\Leb^2(\Xset_{qr})}^2 + c M r^{2s}\Bigr\} 
	\end{align*}
	where the last inequality follows from Lemma~\ref{lem:expected_difference_boundary}. Since $f \in H^{s}(\Xset)$ for $s = 2(q - 1) + 2$, Lemma~\ref{lem:expected_difference_sobolev} allows us to upper bound $\norm{\Delta_r^{q - 1}f}_{\Leb^2(\Xset_{(q - 1)r})}$, which we use to obtain the upper bound
	\begin{align}
	\norm{\Delta_r^qf}_{\Leb^2(\Xset_{qr})} & = \norm{\Delta_r(\Delta_r^{q - 1}f)}_{\Leb^2(\Xset_{qr})} \nonumber \\
	& \leq \Bigl\|\Delta_r\Bigl(\Delta_r^{q - 1}f - r^{2(q - 1)}I_{2e_1}^q\Delta_p^{q - 1}f\Bigr)\Bigr\|_{\Leb^2(\Xset_{qr})} +  r^{2(q - 1)}I_{2e_1}^q\Bigl\|\Delta_r\Bigl(\Delta_p^{q - 1}f\Bigr)\Bigr\|_{\Leb^2(\Xset_{qr})} \nonumber \\ 
	& \leq c \Bigl\|\Delta_r^{q - 1}f - r^{2(q - 1)}I_{2e_1}^q\Delta_p^{q - 1}f\Bigr\|_{\Leb^2(\Xset_{(q - 1)r})} +  c r^{s}I_{2e_1}^q\Bigl\|\Delta_p^{q - 1}f\Bigr\|_{H^2(\Xset_{(q - 1)r})} \nonumber \\
	& \leq c M r^s
	\end{align}
	with the second inequality following from~\eqref{eqn:norm_expected_difference_operator}. There are at most $O(n^{s + 1})$ such terms, hence the overall contribution of these terms to the expectation~\eqref{pf:graph_sobolev_seminorm} is $O(n^{s + 1}r^{s(d + 2)})M^2$.

	Otherwise $\abs{k \cup \ell \cup i} = I < 2q + 1$. By Lemma~\ref{lem:expected_difference_lower_order_1} the total contribution of such terms inside the sum~\eqref{pf:graph_sobolev_seminorm} is $O(n^{I}r^{d(I - 1) + 2}) M^2$; by assumption $r \geq n^{-1/d}$, and therefore this increases with $I$. Taking $I = s$ to be the largest integer less than $s + 1$, the contribution of these terms to the sum is therefore $O(n^sr^{d(s - 1) + 2})M^2$, which in light of the restriction $r \geq n^{-1/(2(s - 1) + d)}$ is $O(n^{s+1}r^{s(d +2)})M^2$.
\end{proof}

>>>>

In this week's notes, I state and prove all results regarding graph Sobolev semi-norms that we need for our graph regression work. These notes make their way into Section 3 (theorem statements and remarks) and Appendix B (proofs) of our graph regression document.

@@

When $s > 1$, in order to obtain the desired upper bound on the graph Sobolev semi-norm we must make some additional assumptions regarding the behavior of $f_0$ near the boundary of $\Xset$, as well as on the smoothness of the density function $p$.
\begin{theorem}
	\label{thm:graph_sobolev_seminorm}
	For some integer $s > 1$, suppose that the density $p \in C^{s - 1}(\Xset,p_{\max})$ and $f \in H_0^s(\Xset,M)$, and additionally that the domain $\Xset$ is Lipschitz. Let $r = r(n)$ be a sequence of connectivity radii satisfying $r(n) \to 0$ and $r(n) \gtrsim n^{-1/(2(s - 1) +d)}$ as $n \to \infty$. Then for all $n$ sufficiently large, there exists a constant $C > 0$ which may depend only on $\Xset$ and $d$ such that
	\begin{equation}
	\label{eqn:graph_sobolev_seminorm}
	f^T \Lap_{n,r}^s f \leq \frac{C}{\delta} n^{s + 1} r^{s(d + 2)}M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{theorem}
A few remarks:
\begin{itemize}
	\item \textbf{Explain why~\eqref{eqn:graph_sobolev_seminorm} should be familiar, and a lower bound on $r$ expected.} The scaling (in $n$, $r$, and $M$) on the right hand side of~\eqref{eqn:graph_sobolev_seminorm} will be familiar to the informed reader. For sufficiently regular functions $f$, it is known \textcolor{red}{(references)} that $\frac{1}{nr^{d + 2}}\Lap_{n,r}f \to \Delta_pf$ for \textcolor{red}{$r \geq ???$}. In that light, it is perhaps reasonable to hope that when $r$ is sufficiently large, some recursive argument yields
	\begin{equation*}
	\Bigl(\frac{1}{nr^{d + 2}}\Lap_{n,r}\Bigr)^s f \to \Delta_p^qf \Longrightarrow \frac{1}{n^{s + 1} r^{s(d + 2)}} f^T \Lap_{n,r}^s f \to \int_{\Xset} f(x) \cdot  \Delta_p^qf(x) p(x) \,dx \leq c M^2.
	\end{equation*}
	\item \textbf{Explain why the actual proof is more subtle.}
\end{itemize}
The proof of Theorem~\ref{thm:graph_sobolev_seminorm} will be considerably longer than that of Lemma~\ref{lem:first_order_graph_sobolev_seminorm}. In anticipation of this proof, it will be helpful to introduce some notation. For $j \in [n]$ and a function $f: \Xset \to \Reals$, define the weighted difference operator $D_jf: \Xset \to \Reals$ to be
\begin{equation*}
\bigl(D_jf\bigr)(x) = \bigl(f(X_j) - f(x)\bigr) \frac{K_r(X_j,x)}{r^d},
\end{equation*}
and for $k \in [n]^q$ for some $q \in \mathbb{N}$, define the iterated difference operator $D_{jk}f: \Xset \to \Reals$ via the recursive relation
\begin{equation*}
\bigl(D_{jk}f\bigr)(x) = \bigl(D_j \circ D_kf\bigr)(x)
\end{equation*}
The matrix $\Lap_{n,r} \in \Reals^{n \times n}$ can then be extended to an operator over $C^{\infty}(\Xset)$, which in an abuse of notation\footnote{We repeat notation because it results in \eqref{eqn:graph_Laplacian_out_of_sample} agreeing with \textcolor{red}{(2)} in-sample, i.e. $\bigl(\Lap_{n,r}^qf\bigr)(X_i) = (\Lap_{n,r}^qf)_i$ for all $i \in [n]$.} we also denote by $\Lap_{n,r}$,
\begin{equation*}
\frac{1}{r^d}\bigl(\Lap_{n,r}f\bigr)(x) := -\sum_{j = 1}^{n} \bigl(D_jf\bigr)(x)
\end{equation*}
so that
\begin{equation}
\label{eqn:graph_Laplacian_out_of_sample}
\frac{1}{r^{dq}}\bigl(\Lap_{n,r}^qf\bigr)(x) = (-1)^q \sum_{k \in [n]^q} \bigl(D_kf\bigr)(x).
\end{equation} 
Consequently, a few standard computations show that the graph Sobolev semi-norm can be written as 
\begin{equation}
\label{eqn:graph_sobolev_seminorm_1}
f^T \Lap_{n,r}^s f = r^{ds} \cdot
\begin{dcases}
\sum_{i = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \bigl(D_kf\bigr)(X_i) \cdot \bigl(D_\ell f\bigr)(X_i),~~ & \textrm{if $s$ is even, for $q = s/2$} \\
\frac{1}{r^d}\sum_{i,j = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \bigl(d_jD_kf\bigr)(X_i) \cdot \bigl(d_jD_{\ell}f\bigr)(X_i) \cdot K_r(X_i,X_j),~~ & \textrm{if $s$ is odd, for $q = (s - 1)/2$}
\end{dcases}
\end{equation}
where $\bigl(d_jf\bigr)(x) := f(X_j) - f(x)$ is the simple difference operator.

@@

\begin{lemma}
	\label{lem:expected_difference_sobolev}
	Let $q \geq 1$ and $s \geq 2q + 1$ be integers. The iterated expected weighted difference operator  $\Delta_r^qf(x) = \Ebb[D_kf(x)]$ for any $k \in (n)^q$. If $f \in H^s(\Xset,M)$ and $p \in C^{s-1}(\Xset,M)$,
	\begin{equation*}
	\Bigl\|\Delta_r^qf - \bigl(r^{2q} I_{2e_1}^{q}\bigr) \Delta_{p}^qf\Bigr\|_{\Leb^2(\Xset_{qr})} \leq CM \cdot
	\begin{dcases}
	r^{2q + 1},& ~~\textrm{if $s = 2q + 1$} \\
	r^{2q + 2},& ~~\textrm{if $s = 2q + 2$}
	\end{dcases}
	\end{equation*}
	where $\Xset_{qr} = \{x \in \Xset: B(x,qr) \subset \Xset\}$, and we recall that $\Delta_pf = -\frac{1}{2p}\mathrm{div}(p^2 \nabla f)$ is the density weighted Laplace operator.
\end{lemma}
\begin{lemma}
	\label{lem:expected_difference_boundary}
	Let $q \geq 1$ and $s \geq 1$ be integers. If $f \in H_0^s(\Xset,M)$ and \textcolor{red}{$p$ satisfies (P2)}, then for all $r > 0$ sufficiently small,
	\begin{equation*}
	\norm{\Delta_r^qf}_{\Leb^2(\Xset^{qr})} \leq cMr^s
	\end{equation*}
	where $\Xset^{qr} = \Xset \setminus \Xset_{qr}$.
\end{lemma}
\begin{lemma}
	\label{lem:expected_difference_lower_order_1}
	Let $I = \abs{k \cup \ell \cup i} < 2q + 1 = s + 1$ for given index vectors $k,\ell \in [n]^q$ and index $i \in [n]$. If $f \in H^1(\Xset)$ for $\Xset$ a Lipschitz domain, and \textcolor{red}{$p$ satisfies (P2)}, then, 
	\begin{equation*}
	\Bigl|\Ebb\Bigl[\bigl(D_kf\bigr)(X_i) \cdot \bigl(D_{\ell}f\bigr)(X_i)\Bigr]\Bigr| \leq C r^{2 + d(I - (s + 1))} \abs{f}_{H^1(\Xset)}^2
	\end{equation*}
	for a constant $C$ which does not depend on $f$.
\end{lemma}
\begin{lemma}
	\label{lem:expected_difference_lower_order_2}
	Let $I = \abs{k \cup \ell \cup i \cup j} < 2q + 2 = s + 1$ for given index vectors $k,\ell \in [n]^q$ and indices $i,j \in [n]$. If $f \in H^1(\Xset)$ for $\Xset$ a Lipschitz domain, and \textcolor{red}{$p$ satisfies (P2)}, then, 
	\begin{equation*}
	\Bigl|\Ebb\Bigl[\bigl(d_jD_kf\bigr)(X_i) \cdot \bigl(d_jD_{\ell}f\bigr)(X_i) \cdot K_r(X_i,X_j)\Bigr]\Bigr| \leq C r^{2 + d(I - s))} \abs{f}_{H^1(\Xset)}^2
	\end{equation*}
	for a constant $C$ which does not depend on $f$.
\end{lemma}
A few remarks:
\begin{itemize}
	\item In~\textcolor{red}{Garcia-Trillos19}, results similar to Lemma~\ref{lem:expected_difference_sobolev} were shown, as part of the proof of pointwise convergence of the graph Laplacian $\Lap_{n,r}$ to $\Delta_p$. Those results specialize to the case $q = 1$ and $s = 3$, and assume the function $f$ is bounded in the relevant Holder rather than Sobolev norm, sufficient for their purposes but not for our own. 
	\item When the function $f$ lacks sufficiently regularity---i.e. when it has two or fewer bounded derivatives---we can no longer obtain an estimate of  $\Delta_rf$ in terms of $\Delta_pf$. However, we can still show that $\Delta_rf$ is itself bounded. For an open set $V \subseteq \Xset$, if $f \in H^{s}(V,M)$---and when $s = 2$, $p \in C^{1}(\Xset,M)$---then
	\begin{equation}
	\label{eqn:norm_expected_difference_operator}
	\norm{\Delta_rf}_{\Leb^2(V_r)} \leq c r^s \norm{f}_{H^s(V)}
	\end{equation}
	for $V_r = \set{x \in V: B(x,r) \subset V}$. We establish this fact, and bound a few related integrals, in Subsection~\ref{subsec:proof_boundedness_expected_difference_operator}.
	\item \textbf{Discuss how the analysis in \textcolor{red}{Belkin12} could conceivably lead to similar conclusions as Lemma~\ref{lem:expected_difference_boundary} under a milder assumption than zero-trace. Explain why you didn't bother to go down this road.}
\end{itemize}

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:expected_difference_boundary}}]
	When $q = 1$, we can relate the $\Leb^2$ norm of $\Delta_rf$ over $\Xset^r$ to the $\Leb^2$ norm of $f$ over $\Xset^{2r}$, as follows:
	\begin{align*}
	\Bigl\|\Delta_rf\Bigr\|_{\Leb^2(\Xset^r)}^2 & = \int_{\Xset^r} \biggl[\int_{\Xset} \bigl(f(y) - f(x)\bigr)K_r(x,y) p(y) \,dy \biggr]^2 \,dx \\
	& \leq p_{\max}^2 \int_{\Xset^r} \biggl[\int_{\Xset} \bigl(\abs{f(y)} +  \abs{f(x)}\bigr)K_r(x,y) \,dy \biggr]^2 \,dx \\
	& \overset{(i)}{\leq}  p_{\max}^2 K_{\max}^2 \int_{\Xset^r} \biggl[\int_{B(0,1) \cap (\Xset - x)/r} \bigl(\abs{f(zr + x)} +  \abs{f(x)}\bigr)\,dz \biggr]^2 \,dx \\
	& \overset{(ii)}{\leq} 2 p_{\max}^2 K_{\max}^2 \int_{\Xset^r} \nu_d^2 \bigl(f(x)\bigr)^2 \,dx + 2 p_{\max}^2 K_{\max}^2 \nu_d \int_{\Xset^r}\biggl[\int_{B(0,1) \cap (\Xset - x)/r} \bigl(f(zr + x)\bigr)^2\,dz\biggr] \,dx \\
	& \leq 2 p_{\max}^2 K_{\max}^2 \int_{\Xset^r} \nu_d^2 \bigl(f(x)\bigr)^2 \,dx + 2 p_{\max}^2 K_{\max}^2 \nu_d \int_{B(0,1)} \int_{\Xset^r} \bigl(f(zr + x)\bigr)^2\,dz \,dx \\
	& \leq 4 p_{\max}^2 K_{\max}^2 \nu_d^2 \norm{f}_{\Leb^2(\Xset^{2r})}^2
	\end{align*}
	where $(i)$ follows from change of variables and $(ii)$ from Young's and Jensen's inequality. Reasoning by induction, we see that to prove the claim of Lemma~\ref{lem:expected_difference_boundary} it suffices to establish that
	\begin{equation}
	\label{pf:expected_difference_boundary}
	\norm{f}_{\Leb^2(\Xset^{(q + 1)r})}^2 \leq c r^{2s} \norm{f}_{H^s(\Xset)}^2,
	\end{equation}
	and in \ref{subsec:proof_sobolev_norm_boundary} we show that this inequality holds whenever $r > 0$ is sufficiently small.
\end{proof}

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:expected_difference_lower_order_1}}]
	The proof of Lemma~\ref{lem:expected_difference_lower_order_2} will be essentially the same as that of Lemma~\ref{lem:expected_difference_lower_order_1}, and so we include only the proof of the latter.

	We first reduce the problem of upper bounding the iterated difference operator to that of upper bounding a sum of single difference operators. Letting $k = (k_1,\ldots,k_q)$, we can show by induction that the absolute value of the iterated difference operator $\abs{D_kf(X_i)}$ is upper bounded,
	\begin{equation*}
	\abs{D_kf(X_i)} \leq \left(\frac{2K_{\max}}{r^d}\right)^{q-1} \sum_{h \in k \cup i} \abs{D_{k_q}f(X_h)} \cdot \1\Bigl\{G_{n,r}[X_{k \cup i}]~\textrm{is a connected graph} \Bigr\}.
	\end{equation*}
	Therefore, for $\ell = (\ell_1,\ldots,\ell_q)$, the product
	\begin{align}
	& \Bigl|D_kf(X_i)\Bigr| \cdot \Bigl|D_{\ell}f(X_i)\Bigr| \leq \nonumber \\
	&~~ \left(\frac{2K_{\max}}{r^d}\right)^{2(q - 1)} \sum_{h,j \in k \cup \ell \cup i} \Bigl|D_{k_q}f(X_h)\Bigr| \cdot \Bigl|D_{\ell_q}f(X_j)\Bigr| \cdot \1\Bigl\{G_{n,r}[X_{k \cup i}], G_{n,r}[X_{\ell \cup i}]~\textrm{are connected graphs} \Bigr\} =  \nonumber \\
	&~~ \left(\frac{2K_{\max}}{r^d}\right)^{2(q - 1)} \sum_{h,j \in k \cup \ell \cup i} \Big|D_{k_q}f(X_h)\Bigr| \cdot \Bigl|D_{\ell_q}f(X_j)\Bigr| \cdot \1\Bigl\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is a connected graph} \Bigr\} \label{pf:expected_difference_lower_order_1_0}
	\end{align}

	We now break our analysis into three cases, based on the number of distinct indices in $k_q,\ell_q,h,j$. In each case we will obtain the same rate
	\begin{equation*}
	\Ebb\Bigl[\abs{D_{k_q}f(X_h)} \cdot \abs{D_{\ell_q}f(X_j)}\Bigr] = O(r^{(\abs{k \cup \ell \cup i} - 3)d + 2}) \cdot |f|_{H^1(\Xset)}^2,
	\end{equation*}
	and plugging this back in to~\eqref{pf:expected_difference_lower_order_1_0} establishes the desired claim.

	\textit{Case 1: Two distinct indices.}
	Let $k_q = \ell_q = i$, and $h = j$. Using the law of iterated expectation, we obtain
	\begin{align*}
	\Ebb \left[\bigl(D_{i}f(X_j)\bigr)^2 \cdot \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \}\right] &= \Ebb \left[\bigl(D_{i}f(X_j)\bigr)^2 \cdot \Pbb\bigl[\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \} |X_i,X_j\bigr]\right] \\
	& = O(r^{(\abs{k \cup \ell \cup i} - 2)d}) \cdot \Ebb\left[\bigl(D_{i}f(X_j)\bigr)^2\right] \\
	& = O(r^{(\abs{k \cup \ell \cup i} - 3)d}) \cdot \Ebb\left[\bigl(d_{i}f(X_j)\bigr)^2K_r(X_i,X_j)\right] \\
	& = O(r^{(\abs{k \cup \ell \cup i} - 3)d + 2}) \cdot |f|_{H^1(\Xset)}^2
	\end{align*}
	where we established the last equality in the proof of Lemma~\ref{lem:first_order_graph_sobolev_seminorm}.

	\textit{Case 2: Three distinct indices.}
	Let $k_q = \ell_q = i$, for some $i \neq j \neq h$. Using the law of iterated expectation, we obtain
	\begin{align}
	\Ebb \Bigl[ & \abs{D_{i}f(X_j)} \cdot \abs{D_if(X_h)} \cdot \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \}\Bigr] \nonumber \\
	& = \Ebb\Bigl[\abs{D_{i}f(X_j)} \cdot \abs{D_if(X_h)} \cdot \Pbb\bigl[\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \} |X_i,X_j,X_h\bigr]\Bigr] \nonumber \\
	& = O(r^{(\abs{k \cup \ell \cup i} - 3)d}) \cdot \Ebb\Bigl[\abs{D_{i}f(X_j)} \cdot \abs{D_if(X_h)} \Bigr]\nonumber \\
	& = O(r^{(\abs{k \cup \ell \cup i} - 3)d + 2})\cdot|f|_{H^1(\Xset)}^2. \label{pf:expected_difference_lower_order_1_1}
	\end{align}
	where we prove~\eqref{pf:expected_difference_lower_order_1_1} in~\ref{subsec:proof_expected_difference_lower_order}.

	\textit{Case 3: Four distinct indices.}
	Using the law of iterated expectation, we find that
	\begin{align}
	\Ebb\Bigl[ &\abs{D_{k_q}f(X_i)}\cdot{\abs{D_{\ell_q}f(X_j)}} \cdot \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \}\Bigr] \nonumber \\
	& = \Ebb\Bigl[\abs{D_{k_q}f(X_i)}\cdot{\abs{D_{\ell_q}f(X_j)}} \cdot\Pbb\bigl[G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected}|X_i,X_j,X_{k_q},X_{\ell_q}\bigr]\Bigr] \nonumber \\
	& = O(r^{(\abs{k \cup \ell \cup i} - 4)d}) \cdot \Ebb\Bigl[\abs{D_{k_q}f(X_i)}\cdot{\abs{D_{\ell_q}f(X_j)}}\cdot\1\{\norm{X_i - X_j} \leq (2q + 1)r\}\Bigr] \nonumber \\
	& = O(r^{(\abs{k \cup \ell \cup i} - 3)d + 2}) \cdot |f|_{H^1(\Xset)}^2 \label{pf:expected_difference_lower_order_1_2}
	\end{align}
	where we prove~\eqref{pf:expected_difference_lower_order_1_2} in~\ref{subsec:proof_expected_difference_lower_order}.
\end{proof}

\begin{proof}[\textbf{Proof of Theorem~\ref{thm:graph_sobolev_seminorm}}]
	We will divide our proof into two cases: when $s$ is even and when $s$ is odd.
